An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-01 poly-embed-journal/poly-embed-journal.tex
part of 8, part of 1...

%% surrogates are important.  in particular, consistent surrogates. (general intro)
In supervised learning, one tries to learn a hypothesis which fits labeled data by minimizing a target loss function.
Unfortunately, minimizing the target loss directly is typically computationally intractable, especially for discrete prediction tasks like classification, ranking, and structured prediction.
Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
After learning a surrogate hypothesis, a link function then translates back to the target problem.
To ensure the surrogate and link properly correspond to the target problem, the surrogate must also be \emph{consistent}, meaning that minimizing it over enough data and applying the link solves the target problem.

%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
\jessiet{I almost feel like this paragraph should be in reverse order: convex consistent studied, design often ad-hoc, for example top-k, also prediction dimension.  But also we might want to punt on prediction dimension for later.  Shifting; old version in comments.}
%A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
%For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
%Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
%In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
%Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
For example, in top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
However, until now, there has been no unifying framework that moves from a given target problem to a convex consistent surrogate and link.

%% we introduce embeddings (the hero narrative)
To address this state of affairs, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above~\citep{ramaswamy2018consistent}.

%% what we prove / what we do (our research question)
We prove that such an embedding scheme is intimately related to the class of polyhedral (piecewise-linear and convex)\jessiet{need this again?} loss functions.
In particular, every discrete loss is embedded by a polyhedral surrogate.
Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.

@@

\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{restatable}
\begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
  Given any polyhedral loss $L$, let $\ell$ be a discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{restatable}
\noindent
Beyond consistency, we show that any calibrated link gives rise to a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target \citep{frongillo2021surrogate}.

@@

\paragraph{Open directions}
\jessie{Dimensionality, geometry of losses, more applications}
Several open directions of remain.
First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.

>>>>

%% surrogates are important.  in particular, consistent surrogates. (general intro)
In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
Unfortunately, minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
After learning a surrogate hypothesis, a link function then translates back to the target problem.
To ensure the surrogate and link properly correspond to the target problem, the surrogate must be \emph{consistent}, meaning that minimizing the surrogate loss over enough data will also minimize the target loss.

%% designing convex and consistent surrogates is often ad hoc.  often inefficient or not consistent (the gap)
\jessiet{I almost feel like this paragraph should be in reverse order: convex consistent studied, design often ad-hoc, for example top-k, also prediction dimension.  But also we might want to punt on prediction dimension for later.  Shifting; old version in comments.}
%A growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions.
%For example, motivated by structured prediction and other large-label domains, recent work has sought surrogates with low prediction dimension, meaning the dimension of the range of the surrogate hypothesis~\citep{frongillo2015elicitation, ramaswamy2016convex}.
%Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
%In other settings, such as top-$k$ classification, there are many proposed ``hinge-like'' surrogates which are piecewise linear and convex (henceforth, \emph{polyhedral}), which were later proved to be inconsistent~\cite{yang2018consistency}.
%Generally speaking, surrogate design has been ad-hoc, with few tools to construct consistent convex surrogates, and even sparser understanding of what types of surrogates are possible.
While a growing body of work seeks to design and analyze consistent convex surrogates for particular target loss functions, to date much of this work has been ad-hoc.
We lack general tools to methodically construct consistent convex surrogates, much less an understanding of which surrogates will be consistent.
For example, in multiclass and top-$k$ classification, several proposed surrogates were proposed and adopted but later proved to be inconsistent~\cite{yang2018consistency}\raft{need a good ref for multiclass; I'm thinking WW and others}.
This state of affairs is even more dire for structured prediction, where in addition to convexity and consistency, one requires a low \emph{prediction dimension} (the dimension of the surrogate prediction space) as the label set can grow exponentially large.
Clever constructions like the binary-encoded predictions (BEP) surrogate for multiclass classification with an abstain option~\cite{ramaswamy2018consistent}, which achieves logarithmic prediction dimension, are the exception rather than the rule.
In all of these settings, we lack a unifying framework that moves from a given target problem to a convex consistent surrogate and link.

%% we introduce embeddings (the hero narrative)
To address this shortcoming, we introduce a new framework motivated by a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete target loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to $\reals^d$ such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
Common examples of this general construction include hinge loss as a surrogate for 0-1 loss and the BEP surrogate mentioned above~\citep{ramaswamy2018consistent}.

%% what we prove / what we do (our research question)
We prove that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
In particular, every discrete loss is embedded by a polyhedral surrogate.
Moreover, such an embedding gives rise to calibrated link function, and is therefore consistent with respect to the target loss.

@@

\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{restatable}
\begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
  Given any polyhedral loss $L$, let $\ell$ be a discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{restatable}

\raf{ADD: Beyond consistency, we show that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target (\S~\ref{subsec:regret-bounds}).}

@@

\paragraph{Implications and Applications}

As we illustrate in \S~\ref{sec:applications},

\paragraph{Open directions}
\jessie{Dimensionality, geometry of losses, more applications}
Finally, several open theoretical directions remain.
First, while \citet{finocchiaro2020embedding} introduce preliminary lower bounds on embedding dimension (e.g., the lowest $d \in \mathbb{Z}$ such that $L : \reals^d \to \reals_+^\Y$ embeds $\ell$) based on optimality conditions that they derive, it is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, the relationship between embedding dimension and other notions of prediction dimension (e.g., convex calibration dimension, convex elicitation complexity) remains to be understood in dimensions greater than $1$.
